---
title: "Data Products Course Week 4 Project - MTCars Data Set"
author: "Mohamed Ali"
date: "December 16, 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

This presentation is a part of deliverables required for Data Products Course week 4 project.

The application demo built by Shiny and can be found at the URL:
https://mam-moneim.shinyapps.io/ShinyApp/

Source code is at GitHub for the application and presnetation at the URL:
https://github.com/mmonim/Coursera-Data-Products-Week-4-Project

## Web Application

This web application provides user with a slider to select the bin size of MPG (Miles per Gallon) attribute with MTCars dataset. The application (server side) will plot a histogram depicting the frequency of repition of this MPG at the MTCars dataset.

## Cars data set

This isthe data of MTCars Dataset and MPG column where we build a histogram for this across all data at the dataset.

```{r cars, echo = TRUE}
summary(cars)
```

## Sample Layout

```{r, echo=FALSE, message=FALSE}

library(plotly)
data("mtcars")
x <- mtcars[,1]
hist(x, breaks= 20, col='darkgray',border='white',main=paste("Histogram of MPG"),xlab="MPG")
```


